Long-Term Reproducibility through Replication:\\ the ReScience Initiative

### 2017-06-12 draft.tex
Start of discussion of GitHub

>>>>

\subsection*{Publishing on the GitHub platform}

\href{http://github.com/}{GitHub} is a commercial platform for
collaborative software development based on the popular version
control system \href{https://git-scm.com/}{git}. It offers unlimited
free use to Open Source projects, defined as projects whose contents
are accessible to everyone. All ReScience activities are organized
around a few such Open Source projects hosted by GitHub. This is an
unusual choice for a scientific journal, the only other journal hosted
on GitHub being \href{http://joss.theoj.org/}{The Journal of Open
Source Software}. In this section, we discuss the advantages and
problems resulting from this choice, considering both technical and
social issues.

There are clear differences between platforms for software
development, such as GitHub, and platforms for scientific publishing,
such as \href{http://home.highwire.org/}{HighWire}. The latter tend to
be expensive commercial products developed for the needs of large
commercial publishers, although the market is beginning to diversify
with products such as
\href{https://www.episciences.org/}{Episciences}.  More importantly,
to the best of our knowledge, no existing scientific publishing
platform supports the submission and review of code, which is an
essential part of every ReScience article. For this reason, the only
option for ReScience was to adopt a software development platform and
develop a set of procedures that make it usable for scientific
publishing.
